Keyword and Collocation analysis on India-related text of Natural History

### 2023-06-19 paper_quarto.qmd
19/6 update

```{r setup, include=FALSE}
library('tidyverse')
library('mclm')
library('here')
library('kableExtra')
library('dplyr')
library('ggplot2')
library('leaflet')
library('widgetframe')
options(digits = 3)
```

@@

widgetframe::frameWidget(m, width = "100%")

@@

As mentioned, the digitized text with geographical annotation is available through [TOPOSText](https://topostext.org/work/148 "Check Natural History on ToposText") project, I further scraped the full text and exported them in .txt as a \[reference corpus\](#\| label: ref-corpus), and also exported those with annotation of coordinates in a range of indian subcontinent as geographically related texts to India as a \[target corpus\](#tar-corpus). The scraping code can be accessed in the link.

@@

The @ref-corpus consists of all texts in the encyclopedia, divided by paragraphs, has `r prettyNum(n_tokens(ref_flist))` tokens and `r n_types(ref_flist)` types, with the type-token ratio of `r round(n_types(ref_flist)/n_tokens(ref_flist), 2)`.

And the @tar-corpus consists of all text related to Indian subcontinent (with coordinates in range of 8°4'N-37°6'N and 68°7'E to 97°25'E) , has `r prettyNum(n_tokens(tar_flist))` tokens and `r n_types(tar_flist)` types, with the type-token ratio of `r round(n_types(tar_flist)/n_tokens(tar_flist), 2)`.

The tokens are separated by white space and in the analysis of this paper, all the punctuation marks are removed.

@@

```{r}
#| label: tbl-kwtables
#| tbl-cap: Top 30 Keywords of Indian related texts in Natural History
#| tbl-subcap: 
#|  - "Sorted by PMI"
#|  - "Sorted by G_signed"
#| layout-ncol: 2
#| warning: false
#| echo: false

top_scores_kw %>% # also valid for top_scores_colloc
  as_tibble() %>%
  select(type, a, PMI, G_signed) %>% # select 4 columns
  arrange(desc(PMI)) %>%             # sort by PMI (descending) 
  head(30) %>%                       # select top 30 rows
  kbl(col.names = c("Type", "Frequency", "PMI", "(Signed $G^{2}$)"))

top_scores_kw %>% # also valid for top_scores_colloc
  as_tibble() %>%
  select(type, a, PMI, G_signed) %>% # select 4 columns
  arrange(desc(G_signed)) %>%             # sort by PMI (descending) 
  head(30) %>%                       # select top 30 rows
  kbl(col.names = c("Type", "Frequency", "PMI", "(Signed $G^{2}$)"))

@@

@tbl-coltables shows the top 30 keywords in Indian related texts comparing to other context, respectively sorted by PMI and G_signed.

```{r}
#| label: tbl-coltables
#| tbl-cap: Top 30 Collocates of word "India" in Natural History
#| tbl-subcap: 
#|  - "Sorted by PMI"
#|  - "Sorted by G_signed"
#| layout-ncol: 2
#| warning: false

>>>>

```{r setup, include=FALSE}
library('tidyverse')
library('mclm')
library('here')
library('kableExtra')
library('dplyr')
library('ggplot2')
library('leaflet')
options(digits = 3)
```

@@

m

@@

As mentioned, the digitized text with geographical annotation is available through [TOPOSText](https://topostext.org/work/148 "Check Natural History on ToposText") project, I further scraped the full text and exported them in .txt as a \![reference corpus\]{#ref-corpus}, and also exported those with annotation of coordinates in a range of Indian subcontinent as geographically related texts to India as a \![target corpus\]{#tar-corpus}. The scraping code can be accessed in the link.

@@

> The @ref-corpus consists of all texts in the encyclopedia, divided by paragraphs, has `r prettyNum(n_tokens(ref_flist))` tokens and `r n_types(ref_flist)` types, with the type-token ratio of `r round(n_types(ref_flist)/n_tokens(ref_flist), 2)`.
>
> And the @tar-corpus consists of all text related to Indian subcontinent (with coordinates in range of 8°4'N-37°6'N and 68°7'E to 97°25'E) , has `r prettyNum(n_tokens(tar_flist))` tokens and `r n_types(tar_flist)` types, with the type-token ratio of `r round(n_types(tar_flist)/n_tokens(tar_flist), 2)`.
>
> The tokens are separated by white space and in the analysis of this paper, all the punctuation marks are removed.

@@

::: {#tbl-kwtables .panel-tabset}
## Sorted by PMI

```{r}
#| warning: false
#| echo: false

top_scores_kw %>% # also valid for top_scores_colloc
  as_tibble() %>%
  select(type, a, PMI, G_signed) %>% # select 4 columns
  arrange(desc(PMI)) %>%             # sort by PMI (descending) 
  head(30) %>%                       # select top 30 rows
  kbl(col.names = c("Type", "Frequency", "PMI", r"(Signed $G^2$)"))%>% 
  kable_minimal() %>% 
  scroll_box(height = "400px")
```

## Sorted by G_signed

```{r}
#| warning: false
#| echo: false

top_scores_kw %>% # also valid for top_scores_colloc
  as_tibble() %>%
  select(type, a, PMI, G_signed) %>% # select 4 columns
  arrange(desc(G_signed)) %>%             # sort by PMI (descending) 
  head(30) %>%                       # select top 30 rows
  kbl(col.names = c("Type", "Frequency", "PMI", r"(Signed $G^2$)")) %>% 
  kable_minimal() %>% 
  scroll_box(height = "400px")
```
:::

```{r}
#| label: tbl-kwtables1
#| tbl-cap: Top 30 Keywords of Indian related texts in Natural History
#| tbl-subcap: 
#|  - "Sorted by PMI"
#|  - "Sorted by G_signed"
#| layout-ncol: 2
#| warning: false
#| echo: false
#| output: false

top_scores_kw %>% # also valid for top_scores_colloc
  as_tibble() %>%
  select(type, a, PMI, G_signed) %>% # select 4 columns
  arrange(desc(PMI)) %>%             # sort by PMI (descending) 
  head(30) %>%                       # select top 30 rows
  kbl(col.names = c("Type", "Frequency", "PMI", "r (Signed $G^{2}$)"))

top_scores_kw %>% # also valid for top_scores_colloc
  as_tibble() %>%
  select(type, a, PMI, G_signed) %>% # select 4 columns
  arrange(desc(G_signed)) %>%             # sort by PMI (descending) 
  head(30) %>%                       # select top 30 rows
  kbl(col.names = c("Type", "Frequency", "PMI", "r (Signed $G^{2}$)"))

@@

@tbl-coltable_PMI and @tbl-coltable_Gsigned shows the top 30 keywords in Indian related texts comparing to other context, respectively sorted by PMI and G_signed.

::: panel-tabset
## Sorted by PMI

```{r}
#| label: tbl-coltable_PMI
#| tbl-cap-location: top
#| tbl-cap: Top 30 Keywords on Indian Related Text in Natural History (sorted by PMI)
#| warning: false
#| echo: false
top_scores_colloc %>% 
  as_tibble() %>%
  select(type, a, PMI, G_signed) %>% # select 4 columns
  arrange(desc(PMI)) %>%        # sort by G_signed (descending)  
  head(30) %>%                       # select top 30 rows
  kbl(col.names = c("Type", "Frequency", "PMI", "Signed G^2"))%>%
  kable_minimal() %>% 
  scroll_box(height = "400px")

## Sorted by G_signed

```{r}
#| label: tbl-coltable_Gsigned
#| tbl-cap-location: top
#| tbl-cap: Top 30 Keywords on Indian Related Text in Natural History (sorted by G_signed)
#| warning: false
#| echo: false

top_scores_colloc %>% 
  as_tibble() %>%
  select(type, a, PMI, G_signed) %>% # select 4 columns
  arrange(desc(G_signed)) %>%        # sort by G_signed (descending)  
  head(30) %>%                       # select top 30 rows
  kbl(col.names = c("Type", "Frequency", "PMI", "`r (Signed G^2^)`"))%>% 
  kable_minimal() %>% 
  scroll_box(height = "400px")

```
:::

```{r}
#| label: tbl-coltables1
#| tbl-cap: Top 30 Collocates of word "India" in Natural History
#| tbl-subcap: 
#|  - "Sorted by PMI"
#|  - "Sorted by G_signed"
#| layout-ncol: 2
#| warning: false
#| echo: false
#| output: false
